Determining the alternatives for scalar implicature

### 2016-04-26 Paper/Paper.Rmd
fixed problems with example literal and pragmatic listener .png - it was the quotes

```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar \``liked.\" (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \``liked.\""}

@@

@@

compare_indices3 <- which(peloquinFrank_3Alts$words %in% check_words)
for (exp in exps) {
  three_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_3Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices3,
              compareDataName = exp,
              alphas = seq(0, 20, by = 0.1))
  res_table <- rbind(res_table, exp = three_alt_alphas[1, ])
}
compare_indices4 <- which(peloquinFrank_4Alts$words %in% check_words)
for (exp in exps) {
  four_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_4Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices4,
              compareDataName = exp,
              alphas = seq(0, 10, by = 0.1))
  res_table <- rbind(res_table, exp = four_alt_alphas[1, ])
}
compare_indices5 <- which(peloquinFrank_5Alts$words %in% check_words)
for (exp in exps) {
  five_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_5Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices5,
              compareDataName = exp,
              alphas = seq(0, 10, by = 0.1))
  res_table <- rbind(res_table, exp = five_alt_alphas[1, ])
}
res_table$row_num <- seq(1, nrow(res_table))
res_table <- res_table %>% 
  mutate(exp = ifelse(row_num %% 2 == 0, "Human judgments 4-alts", "Human judgments 2-alts"),
         model = ifelse(row_num < 3, "2-alts",
                           ifelse(row_num < 5, "3-alts",
                                  ifelse(row_num < 7, "4-alts", "5-alts"))),
         result = paste0("", round(cor, 2), " (alpha = ", alpha, ")")) %>%
  select(model, result, exp) %>%
  spread(exp, result)

>>>>

@@

```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar 'liked'. (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar 'liked'."}

@@

compare_indices3 <- which(peloquinFrank_3Alts$words %in% check_words)
for (exp in exps) {
  three_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_3Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices3,
              compareDataName = exp,
              alphas = seq(0, 20, by = 0.1))
  res_table <- rbind(res_table, exp = three_alt_alphas[1, ])
}
compare_indices4 <- which(peloquinFrank_4Alts$words %in% check_words)
for (exp in exps) {
  four_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_4Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices4,
              compareDataName = exp,
              alphas = seq(0, 10, by = 0.1))
  res_table <- rbind(res_table, exp = four_alt_alphas[1, ])
}
compare_indices5 <- which(peloquinFrank_5Alts$words %in% check_words)
for (exp in exps) {
  five_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_5Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices5,
              compareDataName = exp,
              alphas = seq(0, 10, by = 0.1))
  res_table <- rbind(res_table, exp = five_alt_alphas[1, ])
}
res_table$row_num <- seq(1, nrow(res_table))
res_table <- res_table %>% 
  mutate(exp = ifelse(row_num %% 2 == 0, "Empirical 4-alts", "Empirical 2-alts"),
         model = ifelse(row_num < 3, "2-alts",
                           ifelse(row_num < 5, "3-alts",
                                  ifelse(row_num < 7, "4-alts", "5-alts"))),
         result = paste0("", round(cor, 2), " (alpha = ", alpha, ")")) %>%
  select(model, result, exp) %>%
  spread(exp, result)
